CRUSE to Safe Cycling in Ireland

### 2023-09-22 paper.qmd
Update formats

# # Uncomment for draft versions:
# format: 
#   html: default
#   docx: default

# Uncomment for formatted version
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super

>>>>

# Uncomment for draft versions:
format: 
  html: default
  docx: default
  pdf: default

# # Uncomment for formatted version
# format:
#   elsevier-pdf:
#     keep-tex: true
#     journal:
#       name: Journal Name
#       formatting: preprint
#       model: 3p
#       cite-style: super
